### 2018-12-14 README.Rmd
pull out combined tests, update README with api changes

```{r iteration}
aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive", 
               weight = "sum", output = "tibble", "TOTAL_E", "WHITE_E", "BLACK_E")
```

@@

```{r intensive}
aw_interpolate(wards, tid = WARD, source = asthma, sid = "GEOID", type = "intensive", 
               weight = "sum", output = "tibble", "ASTHMA")
```

@@

# interpolate
aw_interpolate(wards, tid = WARD, source = combinedData, sid = "GEOID", type = "mixed", 
               weight = "sum", output = "tibble", 
               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"),
               intensive = c("ASTHMA"))
```

@@

```{r sf-output}
aw_interpolate(wards, tid = "WARD", source = race, sid = "GEOID", type = "extensive", 
               weight = "sum", output = "sf", "TOTAL_E", "WHITE_E", "BLACK_E")
```

@@

```{r pipe}
wards %>%
  select(-OBJECTID, -AREA) %>%
  aw_interpolate(tid = WARD, source = race, sid = "GEOID", type = "extensive", 
               weight = "sum", output = "tibble", "TOTAL_E", "WHITE_E", "BLACK_E")
```

>>>>

```{r iteration}
aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", weight = "sum", 
               output = "tibble", extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
```

@@

```{r intensive}
aw_interpolate(wards, tid = WARD, source = asthma, sid = "GEOID", 
               weight = "sum", output = "tibble", intensive = "ASTHMA")
```

@@

# interpolate
aw_interpolate(wards, tid = WARD, source = combinedData, sid = "GEOID",
               weight = "sum", output = "tibble", 
               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"),
               intensive = c("ASTHMA"))
```

@@

```{r sf-output}
aw_interpolate(wards, tid = "WARD", source = race, sid = "GEOID",  
               weight = "sum", output = "sf", 
               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
```

@@

```{r pipe}
wards %>%
  select(-OBJECTID, -AREA) %>%
  aw_interpolate(tid = WARD, source = race, sid = "GEOID", 
               weight = "sum", output = "tibble", 
               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
```
